Composition-climate paper

### 2015-07-07 Composition_Ecology.Rmd
Added the `md` file.

**Table 1.** *Gain and loss of the various forest tree types of interest.*
```{r, results=as.is}
pandoc.table(loss_table, justify = "left", style = 'simple')
```

>>>>

**Table 1.** *Gain and loss of the various forest tree types of interest.*
```{r, results='as.is'}
pandoc.table(loss_table, justify = "left", style = 'simple')
```
